Quantum Hoare Type Theory

### 2020-10-28 ms-paper/ms-paper.tex
simplify ott build

\section{Teleportation}
\label{app:teleport}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi q : Qbit. \Pi a : Qbit
        {q =q (alpha |0\> + beta |1\>) /\ (a, e) =q |\Phi+\>}    -- ie, a is entangled with ghost var e
           (m1, m2) : (Bit o* Bit)
        {  (m1, m2) = 00 /\ e =q (alpha |0\> + beta |1\>)
         \/ (m1, m2) = 01 /\ e =q (alpha |1\> + beta |0\>)
         \/ (m1, m2) = 10 /\ e =q (alpha |0\> - beta |1\>)
         \/ (m1, m2) = 11 /\ e =q (alpha |1\> - beta |0\>)}
      = \q.\a.do (q, a) <= apply CNOT to [q, a];
                 q <= apply H to q;
                 rq <= measure q;
                 ra <= measure a;
                 return (rq, ra)
\end{lstlisting}

>>>>

\section{Teleportation}
\label{app:teleport}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi q : Qbit. \Pi a : Qbit
        {q =q (alpha |0\> + beta |1\>) /\ (a, e) =q |\Phi+\>}    -- a is entangled with ghost var e
           (m1, m2) : (Bit o* Bit)
        {  (m1, m2) = 00 /\ e =q (alpha |0\> + beta |1\>)
         \/ (m1, m2) = 01 /\ e =q (alpha |1\> + beta |0\>)
         \/ (m1, m2) = 10 /\ e =q (alpha |0\> - beta |1\>)
         \/ (m1, m2) = 11 /\ e =q (alpha |1\> - beta |0\>)}
      = \q.\a.do (q, a) <= apply CNOT to [q, a];
                 q <= apply H to q;
                 rq <= measure q;
                 ra <= measure a;
                 return (rq, ra)
\end{lstlisting}
